Containers and R---the Rockerverse and beyond

### 2020-01-10 manuscript.Rmd
remove rize, add dockr and renv, see #35

- [`dockerfiler`](https://github.com/ColinFay/dockerfiler/)
- [`containerit`](https://github.com/o2r-project/containerit/)
- [`dockertest`](https://github.com/traitecoevo/dockertest/)

@@

- [`rize` for Shiny](https://github.com/cole-brokamp/rize)

>>>>

- [`dockerfiler`](https://github.com/ColinFay/dockerfiler/)
- [`containerit`](https://github.com/o2r-project/containerit/)
- [`dockr`](https://github.com/smaakage85/dockr)
- [`dockertest`](https://github.com/traitecoevo/dockertest/)
- [`renv` with Docker](https://rstudio.github.io/renv/articles/docker.html)

@@
